Staged Abstract Interpreters

### 2019-09-03 paper/60_cases.tex
revert to as sign; typo

\paragraph{Original AC}
The analysis presented by \citeauthor{Boucher:1996:ACN:647473.727587} is 0-CFA
for a small CPS language consisting of abstractions, applications, recursion and
primitive operators. Figure \ref{compare_ac_sai} (left) shows the AC
implementation: different syntactic constructs are handled in different functions
(e.g., \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{compCall}, \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{compApp}, etc.).
Before refactoring into AC, these functions would take the store as a
regular argument; now every function returns a value of type \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{CompAnalysis},
which is a function (closure) value that takes and returns stores. After the
first run of analysis, we have traversed the AST and obtained a single closure that
takes a store and returns a store. Therefore, the ASTs are static terms, and the
stores are dynamic terms. Now we can invoke the compiled closure with an initial
store to complete the analysis.

@@

On the other side, our approach does exactly the same thing through staging: the
AST are static, and stores are dynamic, therefore we annotate the type \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{Store}
with \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{Rep} (shown in Figure \ref{compare_ac_sai} (right)). In fact, the only
changes of our approach using LMS framework are the types of \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{Store} to
\lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{Rep[Store]}, since they will be known at the next stage; other parts do not need to change. 
The generated code
will just looks-up and update the store. The functions at current stage are
eliminated in the residual program, therefore we do not generate higher-order
functions, which provides additional performance improvement. Nevertheless,
the support from LMS framework is necessary, such as staging support for \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{Map},
we consider these efforts are reusable and complete orthogonal to the
implementation of analysis.

@@

The timestamp is essentially a finite list of expressions that tracks the $k$
recent calling contexts. The definition of abstract addresses \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{KCFAAddr} is also
changed to contain an identifier and the time when it get allocated, meaning that
this address points to some values under such calling context. If $k$ is 0, we
obtain a monovariant analysis as demonstrated before; if $k > 0$, we obtain a
family of analysis with increasing precision. Note that when $k = 0$, the
address space is statically determined by the set of variables appeared in the
program, and we may exploit it to optimize the generated code. But when $k > 0$,
the address generation happens at the next stage, i.e., analysis time.
\begin{lstlisting}
  type AnsM[T] = RepReaderT[RepStateT[
                   RepStateT[RepSetReaderStateM[Cache, Cache, ?], Time, ?], //add Time with a RepStateT
                 Store, ?], Env, T]
  type Result = (Rep[Set[(Value, Store, Time)]], Rep[Cache])
\end{lstlisting}

We then integrate the timestamp into our monad stack by adding a staged
\lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{StateT} monad. The result type is passingly get updated to contain a set of
tuples, where the time is added.
\begin{lstlisting}
  def tick(e: Expr): AnsM[Unit] = for {
    τ <- get_time; u <- liftM(StateTMonad.put((e::τ).take($k$)))
  } yield u
  def alloc(x: String): AnsM[Addr] = for {
    τ <- get_time
  } yield unit(KCFAAddr(x, τ)) // we use unit to turn a current-stage constant to next-stage value
\end{lstlisting}

Every time when we call the \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{eval} function, we refresh the timestamp by calling
the \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{tick} function, which updates the timestamp in the state monad. The \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{tick}
function is implemented as prepending the current expression being evaluated \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{e}
to the existing calling context, and then taking the first $k$ elements from the list.
The type \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{Config} used in caching is also changed to included the timestamp.

@@

A commonly used technique to improve the running time in control-flow analysis
is store-widening. As shown by \cite{Darais:2015:GTM:2814270.2814308,
DBLP:journals/pacmpl/DaraisLNH17}, store-widening analysis can be easily
implemented in monadic abstract interpreter by swapping the \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{StateT} (for store)
and the \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{SetT} (for nondeterminism). In this section, we show this optimization
is orthogonal to staging and we just need to swap the same \textit{staged}
version of monads. After the adjustment, we have the following monad stack:
\begin{lstlisting}
  type AnsM[T] = RepReaderT[RepSetT[RepStateT[
                   RepReaderT[RepStateT[IdM, Cache, ?], Cache, ?], Store, ?], ?], Env, T]
\end{lstlisting}

@@

Abstract garbage collection is a technique to reclaim unreachable addresses in
the store while doing the abstract interpretation
\cite{Might:2006:IFA:1159803.1159807}. \citet{DBLP:journals/pacmpl/DaraisLNH17}
shows that, for big-step monadic abstract interpreter, we may add a \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{Reader}
monad to track a set of root addresses and compute the reachable addresses every
time when we obtain a value. Here we adopt it with staged monads:
\begin{lstlisting}
  type AnsM[T] = RepReaderT[RepReaderT[
                   RepStateT[RepSetReaderStateM[Cache, Cache, ?], Store, ?],
                 Set[Addr], ?], Env, T] //add a reader monad for Set[Addr]
\end{lstlisting}

The idea of abstract garbage collection is shown in Figure \ref{fixgc}. We modify the \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{fix}
function with caching (from Section \ref{sai}) to \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{fix_gc}, but the caching part
is omitted. Several auxiliary functions are used: \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{ask_root} retrieves the
current root addresses from the monad stack; \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{root} compute the reachable
addresses from a value; and \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{gc} cleans up the store according to the reachable
addresses and returns a new store. For the generic interpreter, we also need to
compute the root addresses for compound expressions, readers may refer to
\cite{DBLP:journals/pacmpl/DaraisLNH17}.

@@

As we have already seen from Section \ref{sai}, and recall that the
primitive operation \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{close} can denote a $\lambda$ term to a next-stage Scala function.  The specializing of the staged abstract interpreter to
$\lambda$ terms is independent to other parts of the analyzed program.
\begin{lstlisting}
  def close(ev: Eval => Ans)(λ: Expr, ρ: Rep[Env]): Rep[Value]
\end{lstlisting}

Consider there is a library that contains a list map function \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{map}:
\begin{lstlisting}
  (define (map xs f) (if (null? xs) '() (cons (f (car xs)) (map (cdr xs) f))))
\end{lstlisting}

The specialization (0CFA and without store-widening) of \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{close} on
\lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{map} generates the following next-stage Scala code, that is, the
function \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{x39}:
\begin{lstlisting}
  val x39 = {(x40: List[Set[AbsValue]],          // argument value list
              x41: Map[Addr, Set[AbsValue]],     // store
              x42: Map[Config, Set[ValSt]],      // in cache
              x43: Map[Config, Set[ValSt]]) =>   // out cache
    val x50 = List[Addr](ZCFAAddr("xs"), ZCFAAddr("f")) // addresses of arguments
    val x51 = x50.zip(x40)                              // addresses paired with their values
    val x61 = x51.foldLeft (x41) { case (x52, x53) =>   // prepare a new store that joins
      val x54 = x53._1;  val x55 = x53._2               //   the arguments and their values
        val x58 = x52.getOrElse(x54, x57)               //   into the latest store, initially x41
        val x59 = x58.union(x55);  x52 + (x54 -> x59) } 
    ... }
\end{lstlisting}

@@

\iffalse
\paragraph{Partially-Static Context} Under a polyvariant analysis (like
$k$-CFA), such summary generated by specializing static analyzer even could do
more for calling context by partially-static data optimization. For example,
consider that we have a library consists of three functions \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{f}, \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{g} and \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{h},
where \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{f} calls \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{g} and \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{h} internally and returns \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{y} finally (we extend the
language to have multiple arguments). \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{g} and \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{h} do not depend on \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{f}. Now we
would like to modularly specialize these functions, starting from \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{f} with an
initial environment containing \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{f}, \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{g} and \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{h}.
\begin{lstlisting}
  def f(a, b, c) = val x = g(a, b); val y = h(x, c);  y
\end{lstlisting}

Since $k$ is bounded to a fixed number, after the analysis running $k$ steps
inside of \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{f}, the calling context will purely depend on the static structure of
our module being analyzed.
\fi

@@

To evaluates an assignment, we first evaluate its right-hand side, and then put
the value into the slot where the address of \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{v} points to. For simplicity, we
elect to make the value of the assignment be an \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{void()} value.
\begin{lstlisting}
case Assign(x, e) =>
  val (v, $\sigma$_*) = ev(e, $\rho$, $\sigma$)
  (void(), put($\sigma$_*, get($\rho$, x), v))
\end{lstlisting}

To evaluates a \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{while} loop statement, we evaluate the condition first. Then
similar to how we treat \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{branch0}, we have a generic \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{branch} function but works
on Boolean values. For the \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{true} branch, we recursively call \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{ev} on a newly
constructed expression \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{Seq(e, While(t, e))} meaning that first evaluates \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{e}
and the repeat the loop. Otherwise, for the other branch, we simply return a
void value and current store.
\begin{lstlisting}
case While(t, e) =>
  val (tv, t$\sigma$) = ev(t, $\rho$, $\sigma$)
  branch(tv, ev(Seq(e, While(t, e)), $\rho$, t$\sigma$), (void(), t$\sigma$))
\end{lstlisting}

@@

Interval domain is a relative simple domain which consists of two numeric
fields, an upper bound and a lower bound. Here we annotate the upper bound and
lower bound fields to be of type \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{Rep[Double]}. The operations such as \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{+} of
two intervals produce a new
\begin{lstlisting}
case class Interval(lb: Rep[Double], ub: Rep[Double]) {
  def +(that: Interval): Interval = that match {
    case Interval(lb_, ub_) => Interval(lb + lb_, ub + ub_)
  }
  ...
}
\end{lstlisting}

>>>>

\paragraph{Original AC}
The analysis presented by \citeauthor{Boucher:1996:ACN:647473.727587} is 0-CFA
for a small CPS language consisting of abstractions, applications, recursion and
primitive operators. Figure \ref{compare_ac_sai} (left) shows the AC
implementation: different syntactic constructs are handled in different functions
(e.g., @compCall@, @compApp@, etc.).
Before refactoring into AC, these functions would take the store as a
regular argument; now every function returns a value of type @CompAnalysis@,
which is a function (closure) value that takes and returns stores. After the
first run of analysis, we have traversed the AST and obtained a single closure that
takes a store and returns a store. Therefore, the ASTs are static terms, and the
stores are dynamic terms. Now we can invoke the compiled closure with an initial
store to complete the analysis.

@@

On the other side, our approach does exactly the same thing through staging: the
AST are static, and stores are dynamic, therefore we annotate the type @Store@
with @Rep@ (shown in Figure \ref{compare_ac_sai} (right)). In fact, the only
changes of our approach using LMS framework are the types of @Store@ to
@Rep[Store]@, since they will be known at the next stage; other parts do not need to change. 
The generated code
will just looks-up and update the store. The functions at current stage are
eliminated in the residual program, therefore we do not generate higher-order
functions, which provides additional performance improvement. Nevertheless,
the support from LMS framework is necessary, such as staging support for @Map@,
we consider these efforts are reusable and complete orthogonal to the
implementation of analysis.

@@

The timestamp is essentially a finite list of expressions that tracks the $k$
recent calling contexts. The definition of abstract addresses @KCFAAddr@ is also
changed to contain an identifier and the time when it get allocated, meaning that
this address points to some values under such calling context. If $k$ is 0, we
obtain a monovariant analysis as demonstrated before; if $k > 0$, we obtain a
family of analysis with increasing precision. Note that when $k = 0$, the
address space is statically determined by the set of variables appeared in the
program, and we may exploit it to optimize the generated code. But when $k > 0$,
the address generation happens at the next stage, i.e., analysis time.
\begin{lstlisting}
  type AnsM[T] = RepReaderT[RepStateT[
                   RepStateT[RepSetReaderStateM[Cache, Cache, ?], Time, ?], //add Time with a RepStateT
                 Store, ?], Env, T]
  type Result = (Rep[Set[(Value, Store, Time)]], Rep[Cache])
\end{lstlisting}

We then integrate the timestamp into our monad stack by adding a staged
@StateT@ monad. The result type is passingly get updated to contain a set of
tuples, where the time is added.
\begin{lstlisting}
  def tick(e: Expr): AnsM[Unit] = for {
    τ <- get_time; u <- liftM(StateTMonad.put((e::τ).take($k$)))
  } yield u
  def alloc(x: String): AnsM[Addr] = for {
    τ <- get_time
  } yield unit(KCFAAddr(x, τ)) // we use unit to turn a current-stage constant to next-stage value
\end{lstlisting}

Every time when we call the @eval@ function, we refresh the timestamp by calling
the @tick@ function, which updates the timestamp in the state monad. The @tick@
function is implemented as prepending the current expression being evaluated @e@
to the existing calling context, and then taking the first $k$ elements from the list.
The type @Config@ used in caching is also changed to included the timestamp.

@@

A commonly used technique to improve the running time in control-flow analysis
is store-widening. As shown by \cite{Darais:2015:GTM:2814270.2814308,
DBLP:journals/pacmpl/DaraisLNH17}, store-widening analysis can be easily
implemented in monadic abstract interpreter by swapping the @StateT@ (for store)
and the @SetT@ (for nondeterminism). In this section, we show this optimization
is orthogonal to staging and we just need to swap the same \textit{staged}
version of monads. After the adjustment, we have the following monad stack:
\begin{lstlisting}
  type AnsM[T] = RepReaderT[RepSetT[RepStateT[
                   RepReaderT[RepStateT[IdM, Cache, ?], Cache, ?], Store, ?], ?], Env, T]
\end{lstlisting}

@@

Abstract garbage collection is a technique to reclaim unreachable addresses in
the store while doing the abstract interpretation
\cite{Might:2006:IFA:1159803.1159807}. \citet{DBLP:journals/pacmpl/DaraisLNH17}
shows that, for big-step monadic abstract interpreter, we may add a @Reader@
monad to track a set of root addresses and compute the reachable addresses every
time when we obtain a value. Here we adopt it with staged monads:
\begin{lstlisting}
  type AnsM[T] = RepReaderT[RepReaderT[
                   RepStateT[RepSetReaderStateM[Cache, Cache, ?], Store, ?],
                 Set[Addr], ?], Env, T] //add a reader monad for Set[Addr]
\end{lstlisting}

The idea of abstract garbage collection is shown in Figure \ref{fixgc}. We modify the @fix@
function with caching (from Section \ref{sai}) to @fix_gc@, but the caching part
is omitted. Several auxiliary functions are used: @ask_root@ retrieves the
current root addresses from the monad stack; @root@ compute the reachable
addresses from a value; and @gc@ cleans up the store according to the reachable
addresses and returns a new store. For the generic interpreter, we also need to
compute the root addresses for compound expressions, readers may refer to
\cite{DBLP:journals/pacmpl/DaraisLNH17}.

@@

As we have already seen from Section \ref{sai}, and recall that the
primitive operation @close@ can denote a $\lambda$ term to a next-stage Scala function.  The specializing of the staged abstract interpreter to
$\lambda$ terms is independent to other parts of the analyzed program.
\begin{lstlisting}
  def close(ev: Eval => Ans)(λ: Expr, ρ: Rep[Env]): Rep[Value]
\end{lstlisting}

Consider there is a library that contains a list map function @map@:
\begin{lstlisting}
  (define (map xs f) (if (null? xs) '() (cons (f (car xs)) (map (cdr xs) f))))
\end{lstlisting}

The specialization (0CFA and without store-widening) of @close@ on
@map@ generates the following next-stage Scala code, that is, the
function @x39@:
\begin{lstlisting}
  val x39 = {(x40: List[Set[AbsValue]],          // argument value list
              x41: Map[Addr, Set[AbsValue]],     // store
              x42: Map[Config, Set[ValSt]],      // in cache
              x43: Map[Config, Set[ValSt]]) =>   // out cache
    val x50 = List[Addr](ZCFAAddr("xs"), ZCFAAddr("f")) // addresses of arguments
    val x51 = x50.zip(x40)                              // addresses paired with their values
    val x61 = x51.foldLeft (x41) { case (x52, x53) =>   // prepare a new store that joins
      val x54 = x53._1;  val x55 = x53._2               //   the arguments and their values
        val x58 = x52.getOrElse(x54, x57)               //   into the latest store, initially x41
        val x59 = x58.union(x55);  x52 + (x54 -> x59) } 
    ... }
\end{lstlisting}

@@

\iffalse
\paragraph{Partially-Static Context} Under a polyvariant analysis (like
$k$-CFA), such summary generated by specializing static analyzer even could do
more for calling context by partially-static data optimization. For example,
consider that we have a library consists of three functions @f@, @g@ and @h@,
where @f@ calls @g@ and @h@ internally and returns @y@ finally (we extend the
language to have multiple arguments). @g@ and @h@ do not depend on @f@. Now we
would like to modularly specialize these functions, starting from @f@ with an
initial environment containing @f@, @g@ and @h@.
\begin{lstlisting}
  def f(a, b, c) = val x = g(a, b); val y = h(x, c);  y
\end{lstlisting}

Since $k$ is bounded to a fixed number, after the analysis running $k$ steps
inside of @f@, the calling context will purely depend on the static structure of
our module being analyzed.
\fi

@@

To evaluates an assignment, we first evaluate its right-hand side, and then put
the value into the slot where the address of @v@ points to. For simplicity, we
elect to make the value of the assignment be an @void()@ value.
\begin{lstlisting}
case Assign(x, e) =>
  val (v, $\sigma$_*) = ev(e, $\rho$, $\sigma$)
  (void(), put($\sigma$_*, get($\rho$, x), v))
\end{lstlisting}

To evaluates a @while@ loop statement, we evaluate the condition first. Then
similar to how we treat @branch0@, we have a generic @branch@ function but works
on Boolean values. For the @true@ branch, we recursively call @ev@ on a newly
constructed expression @Seq(e, While(t, e))@ meaning that first evaluates @e@
and the repeat the loop. Otherwise, for the other branch, we simply return a
void value and current store.
\begin{lstlisting}
case While(t, e) =>
  val (tv, t$\sigma$) = ev(t, $\rho$, $\sigma$)
  branch(tv, ev(Seq(e, While(t, e)), $\rho$, t$\sigma$), (void(), t$\sigma$))
\end{lstlisting}

@@

Interval domain is a relative simple domain which consists of two numeric
fields, an upper bound and a lower bound. Here we annotate the upper bound and
lower bound fields to be of type @Rep[Double]@. The operations such as @+@ of
two intervals produce a new
\begin{lstlisting}
case class Interval(lb: Rep[Double], ub: Rep[Double]) {
  def +(that: Interval): Interval = that match {
    case Interval(lb_, ub_) => Interval(lb + lb_, ub + ub_)
  }
  ...
}
\end{lstlisting}

### 2019-09-03 paper/70_eval.tex
revert to as sign; typo

\paragraph{Benchmarks}
The benchmark programs we used in the experiment are collected from several
previous papers \cite{Johnson:2013:OAA:2500365.2500604, ashley:practical,
DBLP:journals/corr/abs-1102-3676} and existing artifacts
\footnote{https://github.com/ilyasergey/reachability} for control-flow
analysis.  Some of the benchmarks are small programs designed for
experiments, such as the \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{kcfa-worst-}$n$ series, which are intended
to challenge $k$-CFA; while some other benchmarks are from real-world
applications, for examples, the RSA public key encryption algorithm
\lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{rsa}. In the Figure \ref{evaluation_result}, we report the number of
AST node after parsing and desugaring (excluding comments) as a proper
measurement of program size.

>>>>

\paragraph{Benchmarks}
The benchmark programs we used in the experiment are collected from several
previous papers \cite{Johnson:2013:OAA:2500365.2500604, ashley:practical,
DBLP:journals/corr/abs-1102-3676} and existing artifacts
\footnote{https://github.com/ilyasergey/reachability} for control-flow
analysis.  Some of the benchmarks are small programs designed for
experiments, such as the @kcfa-worst-@$n$ series, which are intended
to challenge $k$-CFA; while some other benchmarks are from real-world
applications, for examples, the RSA public key encryption algorithm
@rsa@. In the Figure \ref{evaluation_result}, we report the number of
AST node after parsing and desugaring (excluding comments) as a proper
measurement of program size.
